### 2020-05-20 writeup/transfer.tex
wip

\begin{figure}
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
		\caption{Task model similarity}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
		\caption{\# Source task datapoints}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
		\caption{Same vs. Diff. covariances}
	\end{subfigure}
	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer. (a) Section \ref{sec_dist}: Task model similarities; (b) Section \ref{sec_data}: Source task noise level; (c) Section \ref{sec_covariate}: \todo{covariate shift}.}
	\label{fig_model_shift_phasetrans}
\end{figure}

@@

%\begin{figure}
%	\begin{minipage}{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.9\textwidth]{figures/complementary.eps}
%		\caption{When $\Sigma_1$ and $\Sigma_2$ are complementary. The number of target task data points is $n_2 = 4p$.}
%		\label{fig_te_complement}
%	\end{minipage}
%\end{figure}

>>>>

\begin{figure}
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
		\caption{Task model similarity}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
		\caption{Data size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.31\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
		\caption{Covariate shift}
	\end{subfigure}
	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer. (a) Section \ref{sec_dist}: Task model similarities; (b) Section \ref{sec_data}: Source task noise level; (c) Section \ref{sec_covariate}: \todo{same vs. different covariance matrices}.}
	\label{fig_model_shift_phasetrans}
\end{figure}

@@
